### Monotone

```{r include=FALSE}
IS_README <- exists("IS_README") && IS_README
include_graphic <- function(img_path, is_readme = IS_README) {
  if (is_readme) knitr::include_graphics(img_path)
  else knitr::include_graphics(here::here(img_path))
}
```

Use these functions to automatically create a consistent color palette for your slides, based around a single color.

#### `mono_light()`

A light theme based around a single color.

```{r mono_light}
demo_function_call <- function(f, n_params = 1) {
  cat(sep = "",
    "```r\n",
    paste(substitute(f)), "(",
    if (n_params > 0) paste(collapse = ", ",
      sapply(1:n_params, function(i) {
        paste0(names(formals(f))[i], ' = "', formals(f)[[i]], '"')})),
    ")\n```"
    )
}
demo_function_call(mono_light, 1)
```

`r include_graphic("vignettes/images/example_mono_light.png")`

#### `mono_dark()`

A dark theme based around a single color.

```{r mono_dark}
demo_function_call(mono_dark, 1)
```

`r include_graphic("vignettes/images/example_mono_dark.png")`

#### `mono_accent()`

The default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.).

```{r mono_accent}
demo_function_call(mono_accent, 1)
```

`r include_graphic("vignettes/images/example_mono_accent.png")`

#### `mono_accent_inverse()`

An "inverted" default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.).

```{r mono_accent_inverse}
demo_function_call(mono_accent_inverse, 1)
```

`r include_graphic("vignettes/images/example_mono_accent_inverse.png")`


### Duotone

These themes build from two (ideally) complementary colors.

#### `duo()`

A two-colored theme based on a primary and secondary color.

```{r duo}
demo_function_call(duo, 2)
```

`r include_graphic("vignettes/images/example_duo.png")`

#### `duo_accent()`

The default Xaringan theme with two accent colors.

```{r duo_accent}
demo_function_call(duo_accent, 2)
```

`r include_graphic("vignettes/images/example_duo_accent.png")`

#### `duo_accent_inverse()`

An "inverted" default Xaringan theme with two accent colors.

```{r duo_accent_inverse}
demo_function_call(duo_accent_inverse, 2)
```

`r include_graphic("vignettes/images/example_duo_accent_inverse.png")`

### Solarized

There are also two themes based around the [solarized color palette](http://ethanschoonover.com/solarized), `solarized_light()` and `solarized_dark()`.
For both themes, it is advisted to change the syntax highlighting theme to `solarized-light` or `solarized-dark` (looks great paired or constrasted).

#### `solarized_light()`

```{r solarized_light}
demo_function_call(solarized_light, 0)
```

`r include_graphic("vignettes/images/example_solarized_light.png")`

#### `solarized_dark()`

```{r solarized_dark}
demo_function_call(solarized_dark, 0)
```

`r include_graphic("vignettes/images/example_solarized_dark.png")`


To do this, your YAML header should look more-or-less like this:

```yaml
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: ["xaringan-themer.css"]
    nature:
      highlightStyle: solarized-dark
      highlightLines: true
      countIncrementalSlides: false
```
