---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# xaringanthemer

[xaringan]: https://github.com/yihui/xaringan

Easily style your [xaringan] slides with **xaringanthemer**

## Installation

Currently, this is a work in progress.
Try it yourself:

```r
devtools::install_github("gadenbuie/xaringanthemer")
```

## Make it work

To make it work, add `css: xaringan-themed.css` to your xaringan slides YAML header under `xaringan::moonreader:`

```yaml
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themed.css
```

Then, in the first knitr chunk, try this:

````markdown
```{r setup}`r ""`
options(htmltools.dir.version = FALSE)
library(xaringanthemer)
mono_dark(
  base_color = "#b6174b",
  header_font_google = google_font("Josefin Sans"),
  text_font_google = google_font("Montserrat", "300", "300i"),
  code_font_google = google_font("Droid Mono")
)
```
````

## Monotone Themes

Use these functions to automatically create a consistent color palette for your slides, based around a single color.

- `mono_light()`: A light theme based around a single color

- `mono_dark()`: A dark theme based around a single color

- `mono_accent()`: The default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.)

- `mono_accent_inverse()`: An "inverted" default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.)
