---
title: "Template Variables"
author: "Garrick Aden-Buie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Template Variables}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The following table shows the template variables, their default values in the standard `xaringan` theme, the primary element to which the property is applied, and a brief description of the template variable. 

For example, `background_color` by default sets the `background-color` CSS property of the `.remark-slide-content` class to `#FFF`.

Use this table to find the template variable you would like to modify.
You can also use this table to find the CSS class or element associated with a particular template item.

Note that themes, like `mono_accent()`, have additional parameters, but with any theme function you can override the theme by directly setting the arguments below when calling the theme function.
For example, to use `mono_accent()` with a different slide background color, you can call `mono_accent(background_color = "#abc123")`.

```{r table, results = "asis", echo=FALSE}
source("../R/theme_settings.R")
template_variables$variable <- glue::glue_data(template_variables, "`{variable}`")
template_variables$default <- gsub("[{}]", "", template_variables$default)
template_variables$default <- glue::glue_data(template_variables, "`{default}`")
knitr::kable(template_variables)
```

