**xaringanthemer** includes a number of functions that provide
themed **xaringan** styles.
All of the styling functions start with the `style_` prefix.

The goal of each style function is to 
quickly set up a coordinated color palette for your slides
based on one or two starter colors.
Styles based on one color start with `style_mono_`
and styles based on two colors start with `style_duo_`.
How the starter colors are used is described 
in the final portion of the style function name.
For example, `style_mono_accent()` uses a single color as an accent color.

Note that the colors used below are for demonstration only,
the point of the `style_` functions is for you to choose your own color palette!

If you color palette uses more than two colors,
you can add additional colors with the `colors` argument.
See the [Colors](#colors) section for more information.

### Monotone

```{r include=FALSE}
IS_README <- exists("IS_README") && IS_README
include_graphic <- function(img_path) {
  glue::glue(
    '<img src="https://raw.githubusercontent.com/gadenbuie/', 
    'xaringanthemer/assets/{img_path}" data-external="1" />'
  )
}
```

Use these functions to automatically create a consistent color palette for your slides, based around a single color.

#### `style_mono_light()`

A light theme based around a single color.

```{r style_mono_light}
demo_function_call <- function(f, n_params = 1) {
  cat(sep = "",
    "```r\n",
    paste(substitute(f)), "(",
    if (n_params > 0) paste(collapse = ", ",
      sapply(1:n_params, function(i) {
        paste0(names(formals(f))[i], ' = "', formals(f)[[i]], '"')})),
    ")\n```"
    )
}
demo_function_call(style_mono_light, 1)
```

`r include_graphic("example_mono_light.png")`

#### `style_mono_dark()`

A dark theme based around a single color.

```{r style_mono_dark}
demo_function_call(style_mono_dark, 1)
```

`r include_graphic("example_mono_dark.png")`

#### `style_mono_accent()`

The default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.).

```{r style_mono_accent}
demo_function_call(style_mono_accent, 1)
```

`r include_graphic("example_mono_accent.png")`

#### `style_mono_accent_inverse()`

An "inverted" default xaringan theme with a single color used for color accents on select elements (headers, bold text, etc.).

```{r style_mono_accent_inverse}
demo_function_call(style_mono_accent_inverse, 1)
```

`r include_graphic("example_mono_accent_inverse.png")`


### Duotone

These themes build from two (ideally) complementary colors.

#### `style_duo()`

A two-colored theme based on a primary and secondary color.

```{r style_duo}
demo_function_call(style_duo, 2)
```

`r include_graphic("example_duo.png")`

#### `style_duo_accent()`

The default Xaringan theme with two accent colors.

```{r style_duo_accent}
demo_function_call(style_duo_accent, 2)
```

`r include_graphic("example_duo_accent.png")`

#### `style_duo_accent_inverse()`

An "inverted" default Xaringan theme with two accent colors.

```{r style_duo_accent_inverse}
demo_function_call(style_duo_accent_inverse, 2)
```

`r include_graphic("example_duo_accent_inverse.png")`

### Solarized

There are also two themes based around the [solarized color palette](https://ethanschoonover.com/solarized/), `style_solarized_light()` and `style_solarized_dark()`.
For both themes, it is advisted to change the syntax highlighting theme to `solarized-light` or `solarized-dark` (looks great paired or constrasted).

#### `style_solarized_light()`

```{r style_solarized_light}
demo_function_call(style_solarized_light, 0)
```

`r include_graphic("example_solarized_light.png")`

#### `style_solarized_dark()`

```{r style_solarized_dark}
demo_function_call(style_solarized_dark, 0)
```

`r include_graphic("example_solarized_dark.png")`


To do this, your YAML header should look more-or-less like this:

```yaml
output:
  xaringan::moon_reader:
    css: ["xaringan-themer.css"]
    nature:
      highlightStyle: solarized-dark
      highlightLines: true
      countIncrementalSlides: false
```
