---
title: "Presentation Ninja"
subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Yihui Xie"
  - "Garrick Aden-Buie"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-themer, include=FALSE, eval=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)
```

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

- Click the `Knit` button to compile it;

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.
